---
output:
  pdf_document: default
  html_document: default
---
# COVID19 DATA SET REPORT BY PERFORMING EXPLORATORY DATA ANALYSIS[1st Mar,2021 - 15th Apr,2021]

### DINESH RAJAN R A
### 20CSEG06

__Data is taken from__ 
(https://api.covid19india.org/)

## Importing the csv file
```{r}
d1=read.csv("C:\\Users\\DELL\\Documents\\covid19_chetvl_2021.csv")
```

### To know about the loaded csv file
```{r}
str(d1)
```

### Getting the five point summary of the dataset d1
```{r}
summary(d1)
```

### To view the dataset d1
```{r}
View(d1)
```

### To subset the data with district as the variable
```{r}
c=subset(d1,DISTRICT=="CHENNAI")
```

```{r}
t=subset(d1,DISTRICT=="THIRUVALLUR")
```

### To know about the "c" data which we subsetted
```{r}
str(c)
```

```{r}
str(t)
```

### To get the five point summmary
```{r}
summary(c)
```

```{r}
summary(t)
```

### To view the data c & t
```{r}
View(c)
```

```{r}
View(t)
```


### We further spilit the data into month wise
```{r}
mar_c=c[1:31,]
mar_c
str(mar_c)
summary(mar_c)
```

```{r}
apr_c=c[32:46,]
apr_c
str(apr_c)
summary(apr_c)
```

```{r}
mar_t=t[1:31,]
mar_t
str(mar_t)
summary(mar_t)
```

```{r}
apr_t=t[32:46,]
apr_t
str(apr_t)
summary(apr_t)
```

### to know about month wise data
```{r}
summary(mar_c)
```

```{r}
summary(apr_c)
```
### load the required package for visualization
```{r}
library(lattice)
```

### Histogram

```{r}
histogram(~CONFIRMED.CASES|DATE.2021.,data=apr_t,main="Confirmed cases in april 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="orange")
histogram(~ACTIVE.CASES|DATE.2021.,data=apr_t,main="Active cases in april 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="blue")
histogram(~DECEASED.CASES|DATE.2021.,data=apr_t,main="Deceased cases in april 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="red")
histogram(~RECOVERED.CASES|DATE.2021.,data=apr_t,main="Recovered cases in april 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="green")


histogram(~DECEASED.CASES|DATE.2021.,data=apr_c,main="Deceased cases in april 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="red")
histogram(~RECOVERED.CASES|DATE.2021.,data=apr_c,main="Recovered cases in april 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="green")
histogram(~ACTIVE.CASES|DATE.2021.,data=apr_c,main="Active cases in april 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="blue")
histogram(~CONFIRMED.CASES|DATE.2021.,data=apr_c,main="Confirmed cases in april 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="orange")


histogram(~CONFIRMED.CASES|DATE.2021.,data=mar_t,main="Confirmed cases in march 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="orange")
histogram(~ACTIVE.CASES|DATE.2021.,data=mar_t,main="Active cases in march 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="blue")
histogram(~DECEASED.CASES|DATE.2021.,data=mar_t,main="Deceased cases in march 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="red")
histogram(~RECOVERED.CASES|DATE.2021.,data=mar_t,main="Recovered cases in march 21 (tvl)",breaks=40,
          xlab="CASES",ylab="DAYS",col="green")


histogram(~CONFIRMED.CASES|DATE.2021.,data=mar_c,main="Confirmed cases in march 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="orange")
histogram(~ACTIVE.CASES|DATE.2021.,data=mar_c,main="Active cases in march 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="blue")
histogram(~DECEASED.CASES|DATE.2021.,data=mar_c,main="Deceased cases in march 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="red")
histogram(~RECOVERED.CASES|DATE.2021.,data=mar_c,main="Recovered cases in march 21 (che)",breaks=40,
          xlab="CASES",ylab="DAYS",col="green")
```


### Boxplot
```{r}
boxplot(apr_c$DECEASED.CASES,main="DC in Chennai(april)")
boxplot(apr_c$ACTIVE.CASES,main="AC in Chennai(april)")
boxplot(apr_c$CONFIRMED.CASES,main="CC in Chennai(april)")
boxplot(apr_c$RECOVERED.CASES,main="RC in Chennai(april)")


boxplot(apr_t$DECEASED.CASES,main="DC in Thiruvallur(april)")
boxplot(apr_t$ACTIVE.CASES,main="AC in Thiruvallur(april)")
boxplot(apr_t$CONFIRMED.CASES,main="CC in Thiruvallur(april)")
boxplot(apr_t$RECOVERED.CASES,main="RC in Thiruvallur(april)")

boxplot(mar_c$DECEASED.CASES,main="DC in Chennai(march)")
boxplot(mar_c$ACTIVE.CASES,main="AC in Chennai(march)")
boxplot(mar_c$CONFIRMED.CASES,main="CC in Chennai(march)")
boxplot(mar_c$RECOVERED.CASES,main="RC in Chennai(march)")

boxplot(mar_t$DECEASED.CASES,main="DC in Thiruvallur(march)")
boxplot(mar_t$ACTIVE.CASES,main="AC in Thiruvallur(march)")
boxplot(mar_t$CONFIRMED.CASES,main="CC in Thiruvallur(march)")
boxplot(mar_t$RECOVERED.CASES,main="RC in Thiruvallur(march)")
```

### Scatter plot
```{r}
plot(apr_c$DECEASED.CASES,main="DC in Chennai(april)",xlab="Days",ylab = "Cases",type = "l",col="red")
plot(apr_c$RECOVERED.CASES,main="RC in Chennai(april)",xlab="Days",ylab = "Cases",type = "l",col="green")
plot(apr_c$CONFIRMED.CASES,main="CC in Chennai(april)",xlab="Days",ylab = "Cases",type = "l",col="orange")
plot(apr_c$ACTIVE.CASES,main="AC in Chennai(april)",xlab="Days",ylab = "Cases",type = "l",col="blue")

plot(apr_t$DECEASED.CASES,main="DC in Thiruvallur(april)",xlab="Days",ylab = "Cases",type = "l",col="red")
plot(apr_t$RECOVERED.CASES,main="RC in Thiruvallur(april)",xlab="Days",ylab = "Cases",type = "l",col="green")
plot(apr_t$CONFIRMED.CASES,main="CC in Thiruvallur(april)",xlab="Days",ylab = "Cases",type = "l",col="orange")
plot(apr_t$ACTIVE.CASES,main="AC in Thiruvallur(april)",xlab="Days",ylab = "Cases",type = "l",col="blue")

plot(mar_c$DECEASED.CASES,main="DC in Chennai(march)",xlab="Days",ylab = "Cases",type = "l",col="red")
plot(mar_c$RECOVERED.CASES,main="RC in Chennai(march)",xlab="Days",ylab = "Cases",type = "l",col="green")
plot(mar_c$CONFIRMED.CASES,main="CC in Chennai(march)",xlab="Days",ylab = "Cases",type = "l",col="orange")
plot(mar_c$ACTIVE.CASES,main="AC in Chennai(march)",xlab="Days",ylab = "Cases",type = "l",col="blue")


plot(mar_t$DECEASED.CASES,main="DC in Thiruvallur(march)",xlab="Days",ylab = "Cases",type = "l",col="red")
plot(mar_t$RECOVERED.CASES,main="RC in Thiruvallur(march)",xlab="Days",ylab = "Cases",type = "l",col="green")
plot(mar_t$CONFIRMED.CASES,main="CC in Thiruvallur(march)",xlab="Days",ylab = "Cases",type = "l",col="orange")
plot(mar_t$ACTIVE.CASES,main="AC in Thiruvallur(march)",xlab="Days",ylab = "Cases",type = "l",col="blue")
```

## About this data 

This data is taken from the portal (https://api.covid19india.org/)
This data is of the period [1st March, 2021 to 15th April, 2021]

This data contains the Covid19 cases with number of confirmed,active,recovered and deceased cases in the districts of CHENNAI and THIRUVALLUR

### Working on the data
 We have subsetted the data with districts as a variable
 And with that we have found that we could even more slice the data for taking month wise analysis.
 So, the data is again subsetted for the month MARCH and APRIL.
 
 With the above dataset, it is easier to visualize the data with Histogram, Boxplot and Scatter plot.

## Insights
### CHENNAI
From the data we have visualized, we come to know that in Chennai the rate of confirmed cases have been increased 3 times higher in april than march. Since, we take the first 15 days in april, we compare it with the 1st 15 days of march which is `r quantile(mar_c$CONFIRMED.CASES,.25)` which is way less than `r mean(apr_c$CONFIRMED.CASES)`  

Also, the deceased case in chennai is like the confirmed cases.
In march every day at an avg of `r mean(mar_c$DECEASED.CASES)` deceased cases is registered.
but in April it is increased by 5 times.
Comparing it with March first 15 days we have `r quantile(mar_c$DECEASED.CASES,.25)` but for april it is recorded as `r mean(apr_c$DECEASED.CASES)` which tells the people of chennai district to take necessary precaution and be safe.
The plots also prove us the same information.

### THIRUVALLUR
From the data we have visualized, we come to know that in Thiruvallur the rate of confirmed cases have been increased 5 to 6 times compared to April.
Till March 15th we have `r quantile(mar_t$CONFIRMED.CASES,.25)` cases per day. But in APRIL, we founded out the cases to be `r mean(apr_t$CONFIRMED.CASES)` per day. Which alarms the people and government to think about it.

But the good thing which has been founded out was the Deceased rate to be in controlled. In March, `r quantile(mar_t$DECEASED.CASES,.25)` cases was recorded and in April, it is `r mean(apr_t$DECEASED.CASES)` which is well and truly in control.

Interestingly, we found out that every cases that were recorded during the first 15 days of March was converted into Recovered case. Which is the good thing.

### Comparing the two districts

In chennai it is recorded that `r mean(c$CONFIRMED.CASES)` cases have been positive to covid19 each day, while,  it is 4 times higher than the cases `r mean(t$CONFIRMED.CASES)` recorded in Thiruvallur per day.

The data suggests us that almost every person who tested Covid19 positive during the period of [1st Mar,2021 - 15th Apr,2021] in THIRUVALLUR has been RECOVERED as we have `r mean(t$DECEASED.CASES)` cases of Deceased cases.
--------------------------------------------------------------------------------------------------------------

==============================================================================================================